Management frequency and extinction risk

### 2018-05-10 notebook/ms/SI4.Rmd
More notebook edits

```{r}
image(x = sim_old$LAND[,,3], col = topo.colors(9), xaxt = "n", yaxt = "n");
```

@@

```{r}
sim_old$LAND[1:20,   1:20,  3] <- 2; 
sim_old$LAND[1:20,  21:40,  3] <- 3;
sim_old$LAND[1:20,  41:60,  3] <- 4;
sim_old$LAND[1:20,  61:80,  3] <- 5;
sim_old$LAND[1:20,  81:100, 3] <- 6;
sim_old$LAND[21:40,  1:50,  3] <- 7;
sim_old$LAND[21:40, 51:100, 3] <- 8;
sim_old$LAND[41:60,  1:100, 3] <- 9;
sim_old$LAND[61:100, 1:100, 3] <- 1; # Public land
image(x = sim_old$LAND[,,3], col = topo.colors(9), xaxt = "n", yaxt = "n");
```

>>>>

```{r, fig.cap = "Default position of land ownership by farmers."}
image(x = sim_old$LAND[,,3], col = topo.colors(9), xaxt = "n", yaxt = "n");
```

@@

```{r, fig.cap = "Land ownership by farmers as customised in gmse_apply."}
sim_old$LAND[1:20,   1:20,  3] <- 2; 
sim_old$LAND[1:20,  21:40,  3] <- 3;
sim_old$LAND[1:20,  41:60,  3] <- 4;
sim_old$LAND[1:20,  61:80,  3] <- 5;
sim_old$LAND[1:20,  81:100, 3] <- 6;
sim_old$LAND[21:40,  1:50,  3] <- 7;
sim_old$LAND[21:40, 51:100, 3] <- 8;
sim_old$LAND[41:60,  1:100, 3] <- 9;
sim_old$LAND[61:100, 1:100, 3] <- 1; # Public land
image(x = sim_old$LAND[,,3], col = topo.colors(9), xaxt = "n", yaxt = "n");
```

### 2018-05-10 notebook/ms/SI6.Rmd
More notebook edits

```{r, fig.height = 5}
ext_risk1 <- sum(gmse_reps1[,2] < 20);
ext_risk2 <- sum(gmse_reps2[,2] < 20);
ext_risk3 <- sum(gmse_reps3[,2] < 20);
ext_risk4 <- sum(gmse_reps4[,2] < 20);
ext_risk5 <- sum(gmse_reps5[,2] < 20);
y_var     <- c(ext_risk1, ext_risk2, ext_risk3, ext_risk4, ext_risk5);
x_var     <- 1:5;
plot(x = x_var, y = y_var, type = "b", pch = 20, lwd = 2, cex = 1.5,
     xlab = "Management every N time steps (manage_freq)",
     ylab = "Freq. of population extinction", cex.lab = 1.25)
```

>>>>

```{r, fig.height = 5, fig.cap = "Extinction risk given an increasing number of time steps between updating policy decisions for culling costs in a simulated population. Higher values on the x-axis correspond to more time passing before a new policy is set. For each point, a total of 10 replicate simulations were run."}
ext_risk1 <- sum(gmse_reps1[,2] < 20);
ext_risk2 <- sum(gmse_reps2[,2] < 20);
ext_risk3 <- sum(gmse_reps3[,2] < 20);
ext_risk4 <- sum(gmse_reps4[,2] < 20);
ext_risk5 <- sum(gmse_reps5[,2] < 20);
y_var     <- c(ext_risk1, ext_risk2, ext_risk3, ext_risk4, ext_risk5);
x_var     <- 1:5;
plot(x = x_var, y = y_var, type = "b", pch = 20, lwd = 2, cex = 1.5,
     xlab = "Management every N time steps (manage_freq)",
     ylab = "Freq. of population extinction", cex.lab = 1.25)
```
